\chapter{Post Development Testing}

    \section{Stakeholder Feedback}

        Since the cycles were developed separately, with no overlapping functionality, it made sense to have stakeholders test the functionality of each cycle separately. 

        Stakeholders were interviewed regarding their opinions on each cycle and their opinions are listed below.

        \subsection{Cycle 1}
            % Was good to have an installer as that allowed to updates
            % Open source good
            % Good that it's easy to install as it allows it to be more accessible
            % The User Interface could have been designed better (more consistently)

            All stakeholders appreciated how hosting the code for the program on a service such as GitHub made it easier to receive updates as development continued. 
            GitHub was also complimented, as it allows for the community of users to keep track of issues and documentation. 
            Most also appreciated the fact that it was open source, which made it easier for other people to develop the program further, being able to add their own components that suited their particular needs. 

            However, there were complaints about the design of the user interface. Stakeholders said that it was inconsistent and at first looked confusing to use. 
            Although all stakeholders managed to use the installer successfully, one raised a point about GitHub being possibly overwhelming for a person who isn't particularly familiar with the website or computers in general. 


        \subsection{Cycle 2}
            % Good to be able to keep track of projects
            % Useful error communication
            % More consistent UI, better spacing

            Stakeholders appreciated being able to keep track of their projects, as it allowed for multiple things to be worked on at the same time. 
            The error communication was also found to be useful.
            In particular, the user interface was found to be much better than in the previous cycle, with it being more consistent and thought out.


        \subsection{Cycle 3}
            % The core-idea behind the placement of components seems good and intuitive
            % Can't see where components have been placed
            % More components
            % Support for circuits to be built in parallel
            % Support for voltmeters
            % Ammeter configuration good
            % Meter output good

            Stakeholders agree that the core mechanic behind placing components was very intuitive and should be kept going forwards. 
            The user interface for the configuration of the ammeter was good, stakeholders appreciated being able to name the ammeters to keep track of their meters, as well as being able to change the units in order to suit specific applications better. 
            The output of the values on the meters was good. 
            
            However, not being able to see where the components are after they're placed was a great hindrance in being able to keep track of larger circuits.
            Stakeholders said that not being able to customise other components and not being able to make circuits in parallel limited the circuits they could make
            Voltmeters would have also been useful to being able to analyse circuits. 